Atypical Lyman-$\alpha$ emission in a dwarf galaxy via multiphase gas and rotation.

### 2017-01-19 paper/letter.tex
sections

\section{\tol}

@@

\subsection{Rotation Model}

@@

\subsection{Multiphase Model}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.7\textwidth]{CLARA-TOL-main.pdf}
\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

@@

\section{Interpretation}

\subsection{Dynamical Mass Estimates}

@@

\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
\citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
the baryonic mass, depending if one considers the multiphase or
rotation estimate.

>>>>

\section{Observations}

@@

\subsection{Rotation}

@@

\subsection{Multiphase ISM}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.7\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

@@

\section{Discussion}

@@

\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$. 
\citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
the baryonic mass, depending if one considers the multiphase or
rotation estimate.
